### 2016-05-20 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edit to intro of gas burner exp report
Re-numbered/added fan icon to test event drawings for gas burner exp report

The development and behavior of compartment fires, such as a fire inside a residential structure, depend greatly on the ventilation conditions within the compartment. There are a variety of tactics used by firefighters that can affect the ventilation of a fire environment. For example, firefighters may open different doors and windows within a structure or cut holes in a structure's roof with the intention of removing hot gases and smoke from the structure's interior and introducing fresh, cool air into the environment. Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) on the fire ground in an attempt to improve the tenability of the fire environment. PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent. Nine full-scale fire experiments were performed to study how these tactics affect ventilation within a structure. The tests were conducted in two structures designed to replicate typical residential dwellings. During each experiment, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents. During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment. This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(7)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	~(8)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	~(9)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(4)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(5)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(6)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(7)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(8)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(9)~  PPV fan off              			&   21:34		  	&    16:30		\\
	(10) All burners off 						&   22:00		  	&    17:00		\\
	(11) 2nd floor south exterior door opened 	&   23:19		  	&    18:01		\\
	(12) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(13) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ Corner burner on 						& 	2:30 			&	 2:00		\\
	~(2)~ Middle burner on 						&   2:45	  		&	 2:00		\\
	~(3)~ Center burner on 						&   3:00	  		&	 2:00		\\
	~(4)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(5)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(6)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(7)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(8)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(9)~ All burners off 						&   15:00		  	&    14:00		\\
	(10) 2nd floor east double door opened 		&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

The development and behavior of compartment fires, such as a fire inside a residential structure, depend greatly on the ventilation conditions within the compartment. There are a variety of tactics used by firefighters that can affect the ventilation of a fire environment. For example, firefighters may open different doors and windows within a structure or cut holes in a structure's roof with the intention of removing hot gases and smoke from the structure's interior and introducing fresh, cool air into the environment. Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) on the fire ground in an attempt to improve the tenability of the fire environment. PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent.

Nine full-scale fire experiments were performed to study how the tactics described above affect ventilation and the fire environment within a structure. The tests were conducted in two structures designed to replicate typical residential dwellings. During each experiment, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents. During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment. This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(8)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	~(9)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	(10)  Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	(11) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(12) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(13) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(14) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
